---
title: "Data Supporting Participation Rates of GitHub Projects"
output: html_notebook
---

# Initial Setup
```{r}
library(dplyr)
library(bigrquery)

project <- "bonnyci-github-archive"
```

# Measuring Participation

The full participation rates broken down by repo are available in the same data under ci_plunder_events.participation_rate. The data set is huge, hence the summary.

https://bigquery.cloud.google.com:443/savedquery/787787545662:6ad718ecc0a94650b605f2baa0ddd58d

```
SELECT repo_name, num_events, num_actors,
 ROUND(num_events/num_actors, 5) as events_per_actor,
 ROUND((num_events/num_actors)/num_events, 1) as participation_rate
FROM (
  SELECT repo_name,
   count(*) as num_events, 
   EXACT_COUNT_DISTINCT(actor_login) as num_actors,
  FROM [ci_plunder_events.githubarchive_2016_06]
  GROUP BY repo_name
)
```

## What is the proportion of different participation levels in the repository population?

This is a test to see how much variation exists in each category for the number of actors involved in each repository at each participation level.

Summarized for this graph: https://bigquery.cloud.google.com:443/savedquery/787787545662:f1d9cbf5955240af8baf4dc206e508e6

```
SELECT participation_rate, COUNT(repo_name)
FROM [bonnyci-github-archive:ci_plunder_events.total_participation_rate_per_repo]
GROUP BY participation_rate
```

```{r}

participation_rate_sql <- 'select * from [bonnyci-github-archive:ci_plunder_events.participation_rate_summary]'

participation_rate_summary <- query_exec(participation_rate_sql, project = project)

participation_rate_summary <-
    mutate(participation_rate_summary, 
           participation_level = ifelse(participation_rate < 1 & participation_rate > 0, 'Medium', ''))

participation_rate_summary <- 
  mutate(participation_rate_summary, participation_level = ifelse(participation_rate == 0, 'High', participation_level))

participation_rate_summary <-  
  mutate(participation_rate_summary, participation_level = ifelse(participation_rate == 1, 'Low', participation_level))

participation_rate_summary <- participation_rate_summary %>%
  group_by(participation_level) %>%
  summarise(num_actors=sum(num_actors), num_events=sum(num_events), num_repos=sum(num_repos))

saveRDS(participation_rate_summary, "participation_rate_summary.rds")

```

## What proportion of repositories contributed to event activity in each participation level?

Check the distribution of the number of events per repo. Use the rounded result of a log function against number of events to create buckets.

### Low Participation: Events Per Repo Frequency

Calculated here:
https://bigquery.cloud.google.com:443/savedquery/787787545662:8017f4ad2b77472ba85e258b806cea38

```
SELECT repo_name, num_events as event_freq,
round(num_events/95136690, 9) as event_rel_freq
FROM [bonnyci-github-archive:ci_plunder_events.participation_rate_per_repo]
WHERE participation_rate == 1
```

Summarized here:
https://bigquery.cloud.google.com:443/savedquery/787787545662:827535f1ace140e3a87d271da861e263

```
SELECT  event_rel_freq, event_freq, count(repo_name) as num_repos
FROM [bonnyci-github-archive:ci_plunder_events.low_participation_event_freq_repo]
GROUP BY event_rel_freq, event_freq
```


```{r}

low_participation_num_events_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_events.low_participation_events_freq]'

low_participation_num_events_freq <- query_exec(low_participation_num_events_freq_sql, project = project)

low_participation_num_events_freq <- low_participation_num_events_freq %>% 
  mutate(event_freq_log = round(log(event_freq)))

saveRDS(low_participation_num_events_freq, "low_participation_num_events_freq.rds")

```

### Medium Participation: Events Per Repo Frequency

TODO: add links to sql queries

```{r}

med_participation_num_events_freq_sql <- 
  'select * from [bonnyci-github-archive:ci_plunder_events.med_participation_events_freq]'

med_participation_num_events_freq <- query_exec(med_participation_num_events_freq_sql, project = project)
med_participation_num_events_freq <- med_participation_num_events_freq %>% 
  mutate(event_freq_log = round(log(event_freq)))

saveRDS(med_participation_num_events_freq, "med_participation_num_events_freq.rds")

```

### High Participation: Events Per Repo Frequency

TODO: add links to sql queries

```{r}

high_participation_num_events_freq_sql <- 
  'select * from [bonnyci-github-archive:ci_plunder_events.high_participation_events_freq]'

high_participation_num_events_freq <- query_exec(high_participation_num_events_freq_sql, project = project)
high_participation_num_events_freq <- high_participation_num_events_freq %>% 
  mutate(event_freq_log = round(log(event_freq)))

saveRDS(high_participation_num_events_freq, "high_participation_num_events_freq.rds")

```

### All Participation Levels: Events Per Repo Frequency

```{r}
high_participation_num_events_freq <- high_participation_num_events_freq %>% mutate(participation_level = "High")
med_participation_num_events_freq <- med_participation_num_events_freq %>% mutate(participation_level = "Medium")
low_participation_num_events_freq <- low_participation_num_events_freq %>% mutate(participation_level = "Low")

participation_num_events_freq <- bind_rows(high_participation_num_events_freq, med_participation_num_events_freq, low_participation_num_events_freq)

saveRDS(participation_num_events_freq, "participation_num_events_freq.rds")
```


## What was the distribution of actors in each participation level?

### Medium Participation: Actors per Repo Frequency

TODO: add sql

```{r}
med_participation_num_actors_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_events.med_participation_actors_freq]'

med_participation_num_actors_freq <- query_exec(med_participation_num_actors_freq_sql, project = project)
med_participation_num_actors_freq <- med_participation_num_actors_freq %>%
  mutate(actor_freq_log = round(log(actor_freq)))

saveRDS(med_participation_num_actors_freq, "med_participation_num_actors_freq.rds")

```

### High Participation: Actors per Repo Frequency

```{r}

high_participation_num_actors_freq_sql <- 
  'select * from [bonnyci-github-archive:ci_plunder_events.high_participation_actors_freq]'

high_participation_num_actors_freq <- query_exec(high_participation_num_actors_freq_sql, project = project)
high_participation_num_actors_freq <- high_participation_num_actors_freq %>% 
  mutate(actor_freq_log = round(log(actor_freq)))

saveRDS(high_participation_num_actors_freq, "high_participation_num_actors_freq.rds")

```

### All Participation Levels: Actors per Repo Frequency

```{r}
high_participation_num_actors_freq <- high_participation_num_actors_freq %>% mutate(participation_level = "High")
med_participation_num_actors_freq <- med_participation_num_actors_freq %>% mutate(participation_level = "Medium")

# all low participation repos had only 1 unique actor
lp_summary <- participation_rate_summary %>% filter(participation_level == "Low")
low_participation_num_actors_freq <- data.frame(participation_level = "Low", 
                                                actor_rel_freq = 1,
                                                actor_freq = 1,
                                                num_repos = lp_summary$num_repos,
                                                actor_freq_log = 0)

participation_num_actors_freq <- bind_rows(high_participation_num_actors_freq, med_participation_num_actors_freq, low_participation_num_actors_freq)

saveRDS(participation_num_actors_freq, "participation_num_actors_freq.rds")
```

## How does the frequency of event types compare between participation rates?

TODO: add sql

```{r}

participation_rate_event_types_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_events.participation_rate_event_types_summary]'

participation_rate_event_types <- query_exec(participation_rate_event_types_sql, project = project)

participation_rate_event_types <-
    mutate(participation_rate_event_types,
           participation_level = ifelse(participation_rate < 1 & participation_rate > 0, 'Medium', ''))

participation_rate_event_types <-
  mutate(participation_rate_event_types, participation_level = ifelse(participation_rate == 0, 'High', participation_level))

participation_rate_event_types <-
  mutate(participation_rate_event_types, participation_level = ifelse(participation_rate == 1, 'Low', participation_level))

# TODO: change original columns to "num_*" for consistency
# TODO: add number of repos per type
participation_rate_event_types <- participation_rate_event_types %>%
  group_by(participation_level, type) %>%
  summarise(num_actors=sum(total_actors_per_type),
            num_events=sum(total_events_per_type))

participation_rate_event_types <- participation_rate_event_types %>%
  mutate(total_events_per_actor = num_events/num_actors)

saveRDS(participation_rate_event_types, "participation_rate_event_types.rds")

```

# Sampling Experiments

Each population was collected into a table in Google BigQuery and assigned a row number. Sets of random numbers were generated using R's random number function and those records were then downloaded via the Google BigQuery R api.

```{r}

# Better practice would be to have the saveRDS seperate from the functions, but this works for now

get_events_sample <- function(event_type, event_type_abbr) {
  for (i in 1:10){
    events_sql <- paste(
    'SELECT *, rand() as rand
    FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
    WHERE type = "', event_type, '"
    order by rand
    limit 100', sep="")
    events <- query_exec(events_sql, project = project)
    saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
  }
  return(TRUE)
}

get_events_repo_data <- function(event_type_abbr) {
  events_samples <- data.frame()
  events_repo_samples <- data.frame()

  for (i in 1:10){
    events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
    events_sample <- events_sample %>%
      mutate(dataset=paste("sample", i, sep=""))
    events_samples <- bind_rows(events_sample, events_samples)
  
    # Get the actual data for each repo
    sample_sql <-
      paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
            paste(as.character(events_sample$repo_name), collapse="','"),
            "')", sep="")
    sample <- query_exec(sample_sql, project = project)
    sample <- sample %>%
      mutate(dataset=paste("sample", i, sep=""))
    events_repo_samples <- bind_rows(sample, events_repo_samples)
  }
  
  saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
  saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))
  return(events_repo_samples)
}
```


## Push Events
10 random samples of 100 Push events

TODO: add SQL

```{r}
get_events_sample(event_type="PushEvent", event_type_abbr="push")
push_events_repo_samples <- get_events_repo_data(event_type_abbr="push")
```





<h3>Sampling Specific Event Types</h3>
<h4>Experiment 5: 10 random samples of 100 Watch Events</h3>
```{r}
for (i in 1:10){
  watch_events_sql <-
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "WatchEvent"
  order by rand
  limit 100'
  watch_events <- query_exec(watch_events_sql, project = project)

  saveRDS(watch_events, paste("watch_events_sample_", i, ".rds", sep=""))
}

```

```{r}
watch_events_samples <- data.frame()
watch_events_repo_samples <- data.frame()

for (i in 1:10){
  watch_events_sample <- readRDS(paste('watch_events_sample_', i, '.rds', sep=""))
  watch_events_sample <- watch_events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  watch_events_samples <- bind_rows(watch_events_sample, watch_events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(watch_events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  watch_events_repo_samples <- bind_rows(sample, watch_events_repo_samples)
}

saveRDS(watch_events_samples, "watch_events_samples.rds")
saveRDS(watch_events_repo_samples, "watch_events_repo_samples.rds")


```



<h4>Experiment 6: 5 random samples of 100 Pull Request Events</h3>
```{r}
event_type = "PullRequestEvent"
event_type_abbr <- "pr"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```

<h4>Experiment 7: 5 random samples of 100 Create Events</h3>
```{r}
event_type = "CreateEvent"
event_type_abbr <- "create"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```


<h4>Experiment 8: 10 random samples of 100 Member Events</h3>

```{r}
event_type = "MemberEvent"
event_type_abbr <- "member"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```


<h4>Experiment 8: 10 random samples of 100 Release Events</h3>

```{r}
event_type = "ReleaseEvent"
event_type_abbr <- "release"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```
h4>Experiment 8: 10 random samples of 100 Delete Events</h3>

```{r}
event_type = "DeleteEvent"
event_type_abbr <- "delete"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```

h4>Experiment 8: 10 random samples of 100 Public Events</h3>

```{r}
event_type = "PublicEvent"
event_type_abbr <- "public"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```

<h4>Experiment 8: 10 random samples of 100 Issue Comment Events</h3>

```{r}
event_type = "IssueCommentEvent"
event_type_abbr <- "isscomment"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```

<h4>Experiment 8: 10 random samples of 100 Fork Events</h3>

```{r}
event_type = "ForkEvent"
event_type_abbr <- "fork"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```


```{r}
event_type = "IssuesEvent"
event_type_abbr <- "issues"

for (i in 1:10){
  events_sql <- paste(
  'SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_events.githubarchive_2016_06]
  WHERE type = "', event_type, '"
  order by rand
  limit 100', sep="")
  events <- query_exec(events_sql, project = project)

  saveRDS(events, paste(event_type_abbr, "_events_sample_", i, ".rds", sep=""))
}

```

```{r}
events_samples <- data.frame()
events_repo_samples <- data.frame()

for (i in 1:10){
  events_sample <- readRDS(paste(event_type_abbr, '_events_sample_', i, '.rds', sep=""))
  events_sample <- events_sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_samples <- bind_rows(events_sample, events_samples)

  # Get the actual data for each repo
  sample_sql <-
    paste("SELECT * FROM [bonnyci-github-archive:ci_plunder_events.repos_participation_rate_event_types_summary] WHERE repo_name IN('",
          paste(as.character(events_sample$repo_name), collapse="','"),
          "')", sep="")
  sample <- query_exec(sample_sql, project = project)
  sample <- sample %>%
    mutate(dataset=paste("sample", i, sep=""))
  events_repo_samples <- bind_rows(sample, events_repo_samples)
}

saveRDS(events_samples, paste(event_type_abbr, "_events_samples.rds", sep=""))
saveRDS(events_repo_samples, paste(event_type_abbr, "_events_repo_samples.rds", sep=""))

```