---
title: "Sampling Methodlogy Data"
output: html_notebook
---

```{r}
library(dplyr)
library(bigrquery)

project <- "bonnyci-github-archive"
```

# Experiments

## Population

```
SELECT (*) FROM githubarchive:month.201703, githubarchive:month.201702
```

https://bigquery.cloud.google.com:443/savedquery/787787545662:1844b6d0dc164b0ea2103ca2653f5790

```{r}
# TODO time period summary by event type - number of events, number of repos, number of actors, number of independent repos (not part of same user/org)
```


## All Events

### Random Sample of Events

```
SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_repo_samples.2017_02_03_21]
  order by rand
  limit 100
```

https://bigquery.cloud.google.com:443/savedquery/787787545662:743dd041fa9c478ba66dbb336e587cbe

```{r}
all_events_sample_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples.all_events_sample]'

all_events_sample <- query_exec(all_events_sample_sql, project = project)

saveRDS(all_events_sample, "all_events_sample.rds")

```

### Events Data

#### Event Types in Sample

```{r}
all_sample_event_type_freq <- all_events_sample %>%
  group_by(type) %>%
  summarise(num_events = n())

saveRDS(all_sample_event_type_freq, "all_sample_event_type_freq.rds")
```


#### Event Type Frequency per Repository

```{r}
all_repo_event_type_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.ghevents_repo_event_types_frequency]'

all_repo_event_type_freq <- query_exec(all_repo_event_type_freq_sql, project = project)

saveRDS(all_repo_event_type_freq, "all_repo_event_type_freq.rds")
```


#### Actors per Repo
How many unique actors did each repo have?

```{r}
all_repo_actors_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.ghevents_repo_actors_freq]'

all_repo_actors_freq <- query_exec(all_repo_actors_freq_sql, project = project)

saveRDS(all_repo_actors_freq, "all_repo_actors_freq.rds")
```


#### Actors per Event Type per Repo
How many unique actors did each event type in each repo have?

```{r}
all_repo_event_type_actors_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.ghevents_repo_event_type_actors_freq]'

all_repo_event_type_actors_freq <- query_exec(all_repo_event_type_actors_freq_sql, project = project)

saveRDS(all_repo_event_type_actors_freq, "all_repo_event_type_actors_freq.rds")
```

#### Events per Actor Percent Frequency
How are events distributed among actors in the repository?

```{r}
all_repo_e2a_pct_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.ghevents_repo_events_per_actor_pct_freq]'

all_repo_e2a_pct_freq <- query_exec(all_repo_e2a_pct_freq_sql, project = project)

saveRDS(all_repo_e2a_pct_freq, "all_repo_e2a_pct_freq.rds")
```

#### Repos per Owner in Sample
How many separate repos did repo owners in the sample contribute to? Did any actors contribute across samples?

```{r}
all_actor_repo_freq_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.ghevents_actor_repo_freq]'

all_actor_repo_freq <- query_exec(all_actor_repo_freq_sql, project = project)

saveRDS(all_actor_repo_freq, "all_actor_repo_freq.rds")
```

### GitHub API Data

```{r}
all_repo_data_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_data_trimmed]'

all_repo_data <- query_exec(all_repo_data_sql, project = project)

saveRDS(all_repo_data, "all_repo_data.rds")

```

#### Repo Owner Frequency
How many repos came from the same owner?

```{r}
# TODO summary should come from R not GBQ
all_repo_owner_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_owner]'

all_repo_owner <- query_exec(all_repo_owner_sql, project = project)

saveRDS(all_repo_owner, "all_repo_owner.rds")
```


#### Repo Age
How old are the repos in the sample? How recently were they last updated?

I did some exploratory analysis with ratios to see if I could find any interesting patterns but nothing really stuck. One thing I did find is a ratio of age to updated_since that is <1 suggests repos were only acted upon when they were created. There may be further analysis that could be interesting here but I'm not sure that it's telling us anything we can't learn elsewhere.

```{r}
all_repo_age_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_data_age]'

all_repo_age <- query_exec(all_repo_age_sql, project = project)

saveRDS(all_repo_age, "all_repo_age.rds")

```

#### Repo Language Frequency
What languages were represented in the repositories? What proportion of the repository's code was in that language?

```{r}
all_repo_languages_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_languages]'

all_repo_languages <- query_exec(all_repo_languages_sql, project = project)

all_repo_languages <- all_repo_languages %>%
  group_by(repo_slug) %>%
  mutate(
    loc_sum = sum(loc),
    loc_pct = loc/loc_sum,
    loc_log = round(log(loc_pct))
  )

saveRDS(all_repo_languages, "all_repo_languages.rds")

```


#### Releases
What proportion of repos had Releases? How many releases did each repo have? What were the characteristics of repositories that had releases and the ones that didn't?

```{r}
all_repo_releases_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_releases]'

all_repo_releases <- query_exec(all_repo_releases_sql, project = project)

saveRDS(all_repo_releases, "all_repo_releases.rds")

# characteristics of repos with vs without
# age
# number of actors
# events to actor percent
# languages?

```

#### Readme
What proportion of repos had a README detected by Github? What were the characteristics of repositories that had a README and the ones that didn't?

Of those, how many had a Build status tag (indicates possible CI)? What are the characterstics of repositories that had a Build status tag vs those that didn't?

```{r}
all_repo_readme_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_all.repo_readme_buildstatus]'

all_repo_readme <- query_exec(all_repo_readme_sql, project = project)

saveRDS(all_repo_readme, "all_repo_readme.rds")

```


## Push Events

### Random Sample of Events

```
SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_repo_samples.2017_02_03_21]
  where type == "PushEvent"
  order by rand
  limit 100
```

```{r}
push_events_sample_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples.push_events_sample]'

push_events_sample <- query_exec(push_events_sample_sql, project = project)

saveRDS(push_events_sample, "push_events_sample.rds")

```


### Events Data

```{r}
push_events_repo_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.ghevents_repo_summary]'

push_events_repo_summary <- query_exec(push_events_repo_summary_sql, project = project)

saveRDS(push_events_repo_summary, "push_events_repo_summary.rds")

```

```{r}
push_events_repo_type_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.ghevents_repo_type_summary]'

push_events_repo_type_summary <- query_exec(push_events_repo_type_summary_sql, project = project)

saveRDS(push_events_repo_type_summary, "push_events_repo_type_summary.rds")

```

### Github API

```{r}
push_repo_data_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_data_trimmed]'

push_repo_data <- query_exec(push_repo_data_sql, project = project)

saveRDS(push_repo_data, "push_repo_data.rds")

```

```{r}
push_repo_owner_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_owner]'

push_repo_owner <- query_exec(push_repo_owner_sql, project = project)

saveRDS(push_repo_owner, "push_repo_owner.rds")

```


```{r}
push_repo_languages_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_languages]'

push_repo_languages <- query_exec(push_repo_languages_sql, project = project)

saveRDS(push_repo_languages, "push_repo_languages.rds")

```


```{r}
push_repo_age_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_data_age]'

push_repo_age <- query_exec(push_repo_age_sql, project = project)

saveRDS(push_repo_age, "push_repo_age.rds")

```

#### Releases
What proportion of repos had Releases? How many releases did each repo have? What were the characteristics of repositories that had releases and the ones that didn't?

```{r}
push_repo_releases_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_releases]'

push_repo_releases <- query_exec(push_repo_releases_sql, project = project)

saveRDS(push_repo_releases, "push_repo_releases.rds")
```

#### Readme
What proportion of repos had a README detected by Github? What were the characteristics of repositories that had a README and the ones that didn't?

Of those, how many had a Build status tag (indicates possible CI)? What are the characterstics of repositories that had a Build status tag vs those that didn't?

```{r}
push_repo_readme_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_push.repo_readme_buildstatus]'

push_repo_readme <- query_exec(push_repo_readme_sql, project = project)

saveRDS(push_repo_readme, "push_repo_readme.rds")

```

## Watch Events

### Random Sample of Events

```
SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_repo_samples.2017_02_03_21]
  where type == "WatchEvent"
  order by rand
  limit 100
```
### Events Data

```{r}
watch_events_repo_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.ghevents_repo_summary]'

watch_events_repo_summary <- query_exec(watch_events_repo_summary_sql, project = project)

saveRDS(watch_events_repo_summary, "watch_events_repo_summary.rds")

```

```{r}
watch_events_repo_type_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.ghevents_repo_type_summary]'

watch_events_repo_type_summary <- query_exec(watch_events_repo_type_summary_sql, project = project)

saveRDS(watch_events_repo_type_summary, "watch_events_repo_type_summary.rds")

```

### Github API

```{r}
watch_repo_data_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_data_trimmed]'

watch_repo_data <- query_exec(watch_repo_data_sql, project = project)

saveRDS(watch_repo_data, "watch_repo_data.rds")

```

```{r}
watch_repo_owner_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_owner]'

watch_repo_owner <- query_exec(watch_repo_owner_sql, project = project)

saveRDS(watch_repo_owner, "watch_repo_owner.rds")

```


```{r}
watch_repo_languages_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_languages]'

watch_repo_languages <- query_exec(watch_repo_languages_sql, project = project)

saveRDS(watch_repo_languages, "watch_repo_languages.rds")

```


```{r}
watch_repo_age_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_data_age]'

watch_repo_age <- query_exec(watch_repo_age_sql, project = project)

saveRDS(watch_repo_age, "watch_repo_age.rds")

```

```{r}
watch_repo_releases_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_releases]'

watch_repo_releases <- query_exec(watch_repo_releases_sql, project = project)

saveRDS(watch_repo_releases, "watch_repo_releases.rds")
```

```{r}
watch_repo_readme_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_watch.repo_readme_buildstatus]'

watch_repo_readme <- query_exec(watch_repo_readme_sql, project = project)

saveRDS(watch_repo_readme, "watch_repo_readme.rds")

```

## Fork Events

### Random Sample of Events
```
SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_repo_samples.2017_02_03_21]
  where type == "ForkEvent"
  order by rand
  limit 100
```

### Events Data

```{r}
fork_events_repo_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_fork.ghevents_repo_summary]'

fork_events_repo_summary <- query_exec(fork_events_repo_summary_sql, project = project)

saveRDS(fork_events_repo_summary, "fork_events_repo_summary.rds")

```

```{r}
fork_events_repo_type_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_fork.ghevents_repo_type_summary]'

fork_events_repo_type_summary <- query_exec(fork_events_repo_type_summary_sql, project = project)

saveRDS(fork_events_repo_type_summary, "fork_events_repo_type_summary.rds")

```



## Release Events

### Random Sample of Events

```
SELECT *, rand() as rand
  FROM [bonnyci-github-archive:ci_plunder_repo_samples.2017_02_03_21]
  where type == "ReleaseEvent"
  order by rand
  limit 100
```

### Events Data

```{r}
release_events_repo_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_release.ghevents_repo_summary]'

release_events_repo_summary <- query_exec(release_events_repo_summary_sql, project = project)

saveRDS(release_events_repo_summary, "release_events_repo_summary.rds")

```

```{r}
release_events_repo_type_summary_sql <-
  'select * from [bonnyci-github-archive:ci_plunder_repo_samples_release.ghevents_repo_type_summary]'

release_events_repo_type_summary <- query_exec(release_events_repo_type_summary_sql, project = project)

saveRDS(release_events_repo_type_summary, "release_events_repo_type_summary.rds")

```

